---
title: 'Final Project STAT 632 on Multiple Linear Regression'
author: "Arnav K and Maduvanthi C"
date: '2022-04-07'
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## To have a look at the data set-
```{r}
carprice = read.csv("CarPrice_Assignment.csv")
head(carprice)
```
## Full model and it's summary-
```{r}
lm_full <- lm(price ~ doornumber + carbody + fueltype + carlength + horsepower + citympg + highwaympg, data = carprice)
summary(lm_full)
```

## Null model and it's summary-
```{r}
lm_null <- lm(price ~ 1, data = carprice)
summary(lm_null)
```

## Analysis of variance(ANOVA) of the null and the full model-
```{r}
anova(lm_null,lm_full)
```

## The first reduced modlel and it's summary-
## Removed the predictors doornumber and highwaympg from the full model.
```{r}
lm_1 <- lm(price ~ + carbody + fueltype + carlength + horsepower + citympg , data = carprice)
summary(lm_1)
```

## Removed the predictor citympg from model 1.
## Second and the final reduced model and it's summary-
```{r}
lm_2<- lm(price ~ carbody + fueltype + carlength + horsepower, data = carprice)
summary(lm_2)
```

## Residuals vs Fitted Plot-
```{r}
plot(lm_2,which = 1)
```

## Normal Q-Q plot/Scatterplot-
```{r}
plot(lm_2,which = 2)
```

## Analysis of Variance (ANOVA) of the final model and the full model-
```{r}
anova(lm_2,lm_full)
```

## Scatterplot Matrix for the full model-
```{r}
pairs(price ~ factor(doornumber) + factor(carbody) + factor(fueltype) + carlength + horsepower + citympg + highwaympg, data = carprice)
summary(lm_full)
```

## Scatterplot Matrix for the final model-
```{r}
pairs(price ~ factor(carbody) + factor(fueltype) + carlength + horsepower, data = carprice)
```
## Checking all the assumptions for the final model-
```{r}
performance::check_model(lm_2)
```

